university ranking data

### 2025-02-13 inst/universities.Rmd
consistentification
distinguish hankin2017 from hankin2017_rnw
use better magrittr idiom

---
title: "university ranking data"
output: bookdown::html_document2
author: "R. K. S. Hankin"
bibliography: jss_hyper3.bib
---

@@

To cite the `hyper2` package in publications, please use @hankin2017a.
Here I analyse a dataset on NZ university rankings, taken from the
Times Higher Educational Supplement.  First load the data:

@@

Now:
```{r,playerwithadvantage}
universities <- hyper2(pnames=universities_table[1:8,1])
for(i in 2013:2020){universities %<>% `+`(ordertable2supp(f(universities_table,i)))}
universities
```

>>>>

---
title: "university ranking data"
output: bookdown::html_document2
author: "R. K. S. Hankin"
bibliography: hyper2.bib # copy from vignettes/
---

@@

To cite the `hyper2` package in publications, please use @hankin2017_rmd.
Here I analyse a dataset on NZ university rankings, taken from the
Times Higher Educational Supplement.  First load the data:

@@

Now:
```{r,playerwithadvantage}
universities <- hyper2(pnames=universities_table[1:8,1])
for(i in 2013:2020){universities %<>% add(ordertable2supp(f(universities_table,i)))}
universities
```
